Modal Abstractions for Virtualizing Memory Addresses

### 2023-03-23 programlogic.tex
+

\subsection{Address-Space Abstraction}
\label{sec:aspacemodal}
Abstractions we introduce for virtual address spaces are based on the following aspects:
\item a global address space invariant asserting the authorative ownership of the ghost map, $\ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}}$ 
\item for each ghost page-table-walk mapping,  $\sumwalkabs\vaddr\qfrac\paddr$, there exists concrete physical page-table accesses path

>>>>

\subsection{Address-Space Abstraction}
\label{sec:aspacemodal}
Abstractions we introduce for virtual address spaces are based on the following aspects pictorially shown in Figure \ref{fig:logicaladdrspace}:
\begin{enumerate}

\item a global address space invariant (solid round square labelled as $\mathcal{I}$\textsf{ASpace} in Figure \ref{fig:peraspaceinvariant}) asserting the authorative ownership of the ghost map, $\ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}}$ \textit{represents} the full-ownership (solid-round-head arrow) of $\mathcal{A}\textsf{PTableWalk}$
\item per-virtual-pointsto relation ((cutted round square labelled as \textsf{Virtual PointsTo} in Figure \ref{fig:peraspaceinvariant})) asserting the fragmental ownership of the ghost map, $\sumwalkabs\vaddr\qfrac\paddr$ \textit{represents} the fragmental-ownership (cutted-diamond-head arrow) of $\mathcal{A}\textsf{PTableWalk}$
\item for each ghost page-table-walk mapping,  $\sumwalkabs\vaddr\qfrac\paddr$, there exists one shared persistent invariant (shown as double-ended solid arrow 1 to N)
